The Chemistry Development Kit (CDK) \cdkversion{}: atom typing, depiction, molecular formulas, and substructure searching

### 2017-04-27 article.tex
Make stereochemistry citation more prominent and provide the basic description of the aromaticity.

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile\footnote{Molfiles 
  can also store tetrahedral stereochemistry as a parity value, this is read if no coordinates are specified.
  In general there is no guarantee the parity value is read and the only portable way to store
  stereochemistry in a molfile is with coordinates.}, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates 
  can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}.

@@

  % More on performance?
  % http://efficientbits.blogspot.co.uk/2013_10_01_archive.html
  % http://efficientbits.blogspot.co.uk/2013_11_01_archive.html

@@

>>>>

  The perception from coordinates and wedge assignment algorithms are fundamental for conversion
  between formats that store stereochemistry implicitly based on coordinates (e.g. molfile\footnote{Molfiles 
  can also store tetrahedral stereochemistry as a parity value, this is read if no coordinates are specified.
  In general there is no guarantee the parity value is read and the only portable way to store
  stereochemistry in a molfile is with coordinates.}, CML) and 
  explicitly (e.g. SMILES, CML, InChI). Perception from 2D coordinates 
  can optionally identify
  perspective projections, specifically: Fischer, Haworth, and Chair projections. With the perception of 
  perspective projections enabled, database entries currently considered distinct can be merged
  (Figure~\ref{fig:stereoprojections}).  The perception from projections is based on an  algorithm briefly  
  described by~\cite{Karapetyan2015}. Other aspects of stereochemistry handling
  are detailed thoroughly in Chapter 6 of ~\cite{May2015}.

@@

@@

The aromaticity algorithm is straight forward, the potential electron donation
is calculated for each atom as -1 (not aromatic), 0, 1, 2. The set of cycles
provided in the constructor is then generated and each is checked for H{\"u}ckel's 
rule ($4n+2$).
